---
title: "Testes de Hipóteses"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(tigerstats)
knitr::opts_chunk$set(echo = FALSE)
```


## Teste Z

### Exercício 9

<p align = "justify">O fabricante de certa marca de suco informa que as embalagens de seu produto têm em média 500 ml, com desvio padrão igual a 10 ml. Tendo sido encontradas no mercado algumas embalagens com menos de 500 ml, suspeita-se que a informação do fabricante seja falsa. Para verificar se isto ocorre, um fiscal analisa uma amostra de 200 embalagens escolhidas aleatoriamente no mercado e constata que as mesmas contêm em média 498 ml. Considerando-se um nível de significância de 5%, pode-se afirmar que o fabricante está
mentindo? Calcule o valor da prova para esta amostra.</p>


```{r two-plus-two, exercise=TRUE}
sigma <- 10
n <- 200
xbarra <- 498
alpha <- 0.05
mu <- 500
#H0:mu=500
#H1:mu<500 (unilateral a esquerda)

#Estatistica do Teste (teste-z)

Zcal <- (xbarra-mu)/(sigma/sqrt(n))
Zcal
Ztab <- qnorm(0.05, mean = 0, sd = 1, lower.tail = T)
Ztab

Conclusao <- ifelse(abs(Zcal)>abs(Ztab), 
                    paste("Como |Zcal|>|Ztab|, rejeita-se H0 ao nivel de alpha=", alpha, "de significancia"),
                    paste("Como |Zcal|<|Ztab|, não rejeita-se H0 ao nivel de alpha=", alpha, "de significancia"))

Conclusao

pnormGC(Zcal, region = "below", mean = 0, sd = 1, graph = T)

pvalor <- pnorm(Zcal, mean = 0, sd = 1, lower.tail = T)
pvalor
```

### Exercise with Code

*Here's an exercise with some prepopulated code as well as `exercise.lines = 5` to provide a bit more initial room to work.*

Now write a function that adds any two numbers and then call it:

```{r add-function, exercise=TRUE, exercise.lines = 5}
add <- function() {
  
}
```

## Topic 2

### Exercise with Hint

*Here's an exercise where the chunk is pre-evaluated via the `exercise.eval` option (so the user can see the default output we'd like them to customize). We also add a "hint" to the correct solution via the chunk immediate below labeled `print-limit-hint`.*

Modify the following code to limit the number of rows printed to 5:

```{r print-limit, exercise=TRUE, exercise.eval=TRUE}
mtcars
```

```{r print-limit-hint}
head(mtcars)
```

### Quiz

*You can include any number of single or multiple choice questions as a quiz. Use the `question` function to define a question and the `quiz` function for grouping multiple questions together.*

Some questions to verify that you understand the purposes of various base and recommended R packages:

```{r quiz}
quiz(
  question("Which package contains functions for installing other R packages?",
    answer("base"),
    answer("tools"),
    answer("utils", correct = TRUE),
    answer("codetools")
  ),
  question("Which of the R packages listed below are used to create plots?",
    answer("lattice", correct = TRUE),
    answer("tools"),
    answer("stats"),
    answer("grid", correct = TRUE)
  )
)
```

